\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2023-06-21 doc/regime_changes_bp_rr.tex
Additional reviewer response updates

Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}. Each country is given a weight which represents its influence in the synthetic control portfolio. The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.

@@

While conventional wisdom suggests investors dislike political instability, we show that this is not necessarily always the case. Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.

@@

>>>>

Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}. \textcolor{red}{This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event. We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.} Each country is given a weight which represents its influence in the synthetic control portfolio. The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}. \textcolor{red}{In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are [add percentage difference in magnitude] and never significantly different from zero for coups, assassinations, or resignations (or overall).}

@@

While conventional wisdom suggests investors dislike unexpected regime changes, we show that this is not necessarily always the case. Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.

@@

\textcolor{red}{Our findings have a number of potential implications for policymakers. First, our finding that even democratically subversive irregular regime changes can have a positive impact on investment when the replacement government is clearly pro-business  implies that investor goals and actions may be at odds with regime stability. Second, the immediate nature and large magnitude of the financial outflows we observe in the wake of the majority of coups and assassinations suggests that a weakened financial system and economy are likely to accompany these kinds of regime changes. More optimistically, however, we also find suggestive evidence that in the event of a democratic extra-legal regime change, clearly signalling a commitment to democracy may result in increased investment in a country's firms.}
